What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
still 10 pages and we answered those questions!
wording fixes

Based on the labels, and our manual topic labelling, we compared the results of the unsupervised word matching approach. For each quality we tried to assess whether the manual tag matched the unsupervised label assigned. Table \ref{tbl:maxdb-unsup-results} shows our results for MaxDB and MySQL. In general results are poor. Using the F-Measure, the weighted average of precision and recall, where 1 is perfect, our best results are 0.6, a few at 0.4, and most around 0.2. We achieved similar results using the Matthew's correlation coefficient (used to measure efficacy where classes are of different sizes) and ROC.

Based on these results we find that reliability and usability worked well for MaxDB in \textsf{exp2} and better in \textsf{exp3}. MySQL reasonable results within \textsf{exp2} were for reliability and efficiency. MySQL's results for efficiency did not improve in \textsf{exp3} but other qualities such as functionality did improve. If a \emph{C} grade performance has a ROC value of $0.6$ then most of these tests scored \emph{C} or less, but our results were still better than random chance.

\begin{table*}[h]
	\centering

@@

@@

We took our annotated data-set and applied supervised learners to it. Because our data-set was of word counts we expected Bayesian techniques, often used in spam filtering, to perform well. We also tried other learners that WEKA~\cite{weka09} provides: rule learners, tree learners, vector space learners, and support vector machines.  Table \ref{tab:best-learn-per-tag} shows the performance of the best performing learner per label.  We considered the best learner for a label to be the one which had the highest ROC value for that label. Table \ref{tab:best-learn-per-tag} shows the ROC value, the accuracy of a ZeroR learner ( a learner which just chooses the largest category all of the time), the difference in accuracy between the best learner and ZeroR, and the F-measure for that particular learner. The ZeroR difference is often negative, but in particular for labels which are not as common this can be expected because any miscategorization will hurt accuracy, this is why the F1 (F-measure) and the ROC values are useful as they can better present performance on labels which are not applicable to the majority of samples.

Table \ref{tab:best-learn-per-tag} shows that MaxDB and MySQL have quite different results, the ROC values for reliability and functionality seem swapped between projects. It should be noted that for both projects Bayesian techniques did the best out of a wide variety of machine learners tested. Discriminative Multinomial Naive Bayes (DMNBtext), Naive Bayes (NaiveBayes) and Multinomial Naive Bayes (NaiveBayesMultinomal) are all based on Bayes theorem and all assume, naively, that the features are independent. The features we used are word counts per message. One beneficial aspect of this result is that it suggests we can have very fast training and classifying  since Naive Bayes can be calculated in $O(N)$ for $N$ features.
%http://nlp.stanford.edu/IR-book/html/htmledition/naive-bayes-text-classification-1.html

It seems like the smaller the label the harder it is to get accurate results. Although these results seem better than our previous word bag results of \textsf{exp2} and \textsf{exp3} because the ROC values are sufficiently higher in most cases other than MaxDB reliability and MySQL efficiency.

The limitation of the approach we took here is that we only checked independently for each label. Labels could be correlated with each other, as well as we did not evaluate how well the learners performed together.

% Cribbed from: 
% src/validate/latex-out/best-learner-per-project-roc-table.tx
\begin{table*}
\centering
\begin{tabular}{ccc|rrrr}
\toprule
Label & Project & Learner & ROC & ZeroR Acc. & ZeroR. Diff & F1\\
\midrule
portability &  MySQL &  NaiveBayesMultinomial &  0.74 &  58.53 &  11.43 &  0.70  \\ 
efficiency &  MySQL &  NaiveBayes &  0.67 &  93.69 &  -7.68 &  0.88 \\ 
reliability &  MySQL &  NaiveBayes &  0.73 &  83.11 &  -12.80 &  0.74 \\ 
functionality &  MySQL &  DMNBtext &  0.81 &  54.44 &  21.67 &  0.76 \\ 
maintainability &  MySQL &  DMNBtext &  0.78 &  76.62 &  3.41 &  0.75 \\ 
usability &  MySQL &  NaiveBayes &  0.75 &  94.54 &  -5.80 &  0.90  \\ 
%total & MySQL & NaibeBayes & 0.75 & 
 \hline 
portability &  MaxDB &  NaiveBayes &  0.84 &  77.12 &  2.06 &  0.80 \\ 
efficiency &  MaxDB &  NaiveBayes &  0.62 &  88.43 &  -11.31 &  0.79 \\ 
reliability &  MaxDB &  DMNBtext &  0.84 &  89.46 &  3.86 &  0.92  \\ 
functionality &  MaxDB &  NaiveBayes &  0.67 &  91.26 &  -6.94 &  0.86  \\ 
maintainability &  MaxDB &  NaiveBayes &  0.70 &  79.43 &  -9.25 &  0.72  \\ 
usability &  MaxDB &  NaiveBayes &  0.56 &  95.37 &  -4.37 &  0.91  \\ 
 \hline 
\end{tabular}
\caption{Per label, per project, the best learner for that label}
\label{tab:best-learner-per-tag}
\end{table*}

@@

We applied the Mulan~\cite{mulan} library for Multi-Label learning to our data-set because we feel that topics can have more like one label, much like how a revision can have more than one topic. Multi-label learning is more than just classifying entities with more than one label. It also includes methods for determining the performance of such techniques. Consider that the problem has changed, instead of looking at the precision and recall of applying one label, we have to rank multiple labels at once. We have to check if the full subset of labels was applied and then how much of that subset was applied.

Another aspect of multi-label learning is the micro versus macro measurements. Macro measurements are aggregated at a class or label level. Micro measurements are aggregated at a decision level. So a macro-ROC measurement is the average ROC over the ROC values for all labels, where a micro-ROC is the average ROC over all examples that were classified. Unfortunately for MaxDB the macro-ROC values are undefined because of poor performance of one of the labels.

We have presented the results of Mulan's multi-label learners in Table \ref{tab:mulan}.  Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multi-label classifiERs (HOMER), performed the best. HOMER and BR acts as a hierarchy of learners, BR is flat while HOMER tries to build a deeper hierarchy in order to build a more accurate learner~\cite{mulan}. We feel that these classifiers performed better than other multi-label classifiers because they have the best micro and macro ROC scores than the other classifiers although their results seem comparable to the naive Bayesian learners we used in Section \ref{sec:suplabelling}.

@@

Very rarely did \textsf{exp2} and \textsf{exp3} ever perform as well as the machine learners. For MaxDB reliability was slightly better detected using the static word list of \textsf{exp2}. In general, the machine learners and \textsf{exp3} did better than \textsf{exp2} for both MaxDB and MySQL. For both MySQL and MaxDB usability was better served by \textsf{exp2}.

>>>>

Based on the labels, and our manual topic labelling, we compared the results of the unsupervised word matching approach. For each quality we tried to assess whether the manual tag matched the unsupervised label assigned. Table \ref{tbl:maxdb-unsup-results} shows our results for MaxDB and MySQL. In general results are poor. Using the F-Measure, the weighted average of precision and recall, where 1 is perfect, our best results are 0.6, a few at 0.4, and most around 0.2. We achieved similar results using the Matthew's correlation coefficient (used to measure efficacy where classes are of different sizes) and ROC.  
\begin{table*}[h]
	\centering

@@

Based on these results we find that reliability and usability worked well for MaxDB in \textsf{exp2} and better in \textsf{exp3}. MySQL had reasonable results within \textsf{exp2} for reliability and efficiency. MySQL's results for efficiency did not improve in \textsf{exp3} but other qualities such as functionality did improve. If a \emph{C} grade performance has a ROC value of $0.6$ then most of these tests scored \emph{C} or less, but our results were still better than random chance.

@@

We took our annotated data-set and applied supervised learners to it. Because our data-set was of word counts we expected Bayesian techniques, often used in spam filtering, to perform well. We also tried other learners that WEKA~\cite{weka09} provides: rule learners, tree learners, vector space learners, and support vector machines.  Table \ref{tab:best-learn-per-tag} shows the performance of the best performing learner per label.  We considered the best learner for a label to be the one which had the highest ROC value for that label. Table \ref{tab:best-learn-per-tag} uses the ZeroR learner as a baseline, since it naively chooses the largest category all of the time. The ZeroR difference is often negative. For labels which are not as common, this can be expected because any miscategorization will hurt accuracy. This is why the F1 (F-measure) and the ROC values are useful, as they can better present performance on labels which are not applicable to the majority of samples.

Table \ref{tab:best-learn-per-tag} shows that MaxDB and MySQL have quite different results, as the ROC values for reliability and functionality seem swapped between projects. It should be noted that for both projects Bayesian techniques did the best out of a wide variety of machine learners tested. Discriminative Multinomial Naive Bayes (DMNBtext), Naive Bayes (NaiveBayes) and Multinomial Naive Bayes (NaiveBayesMultinomal) are all based on Bayes's theorem and all assume, naively, that the features are independent. The features we used are word counts per message. One beneficial aspect of this result is that it suggests we can have very fast training and classifying  since Naive Bayes can be calculated in $O(N)$ for $N$ features.
%http://nlp.stanford.edu/IR-book/html/htmledition/naive-bayes-text-classification-1.html

The smaller the label the harder it is to get accurate results. Nevertheless, these results are better than our previous word bag results of \textsf{exp2} and \textsf{exp3}, because the ROC values are sufficiently higher in most cases (other than MaxDB reliability and MySQL efficiency).

The limitation of the approach we took here is that we assume labels are independent; however, labels could be correlated with each other. We also did not evaluate how well the learners performed together.

% Cribbed from: 
% src/validate/latex-out/best-learner-per-project-roc-table.tx
\begin{table*}
\centering
\begin{tabular}{ccc|rrrr}
\toprule
Label & Project & Learner & ROC & ZeroR Acc. & ZeroR. Diff & F1\\
\midrule
portability &  MySQL &  NaiveBayesMultinomial &  0.74 &  58.53 &  11.43 &  0.70  \\ 
efficiency &  MySQL &  NaiveBayes &  0.67 &  93.69 &  -7.68 &  0.88 \\ 
reliability &  MySQL &  NaiveBayes &  0.73 &  83.11 &  -12.80 &  0.74 \\ 
functionality &  MySQL &  DMNBtext &  0.81 &  54.44 &  21.67 &  0.76 \\ 
maintainability &  MySQL &  DMNBtext &  0.78 &  76.62 &  3.41 &  0.75 \\ 
usability &  MySQL &  NaiveBayes &  0.75 &  94.54 &  -5.80 &  0.90  \\ 
%total & MySQL & NaibeBayes & 0.75 & 
 \hline 
portability &  MaxDB &  NaiveBayes &  0.84 &  77.12 &  2.06 &  0.80 \\ 
efficiency &  MaxDB &  NaiveBayes &  0.62 &  88.43 &  -11.31 &  0.79 \\ 
reliability &  MaxDB &  DMNBtext &  0.84 &  89.46 &  3.86 &  0.92  \\ 
functionality &  MaxDB &  NaiveBayes &  0.67 &  91.26 &  -6.94 &  0.86  \\ 
maintainability &  MaxDB &  NaiveBayes &  0.70 &  79.43 &  -9.25 &  0.72  \\ 
usability &  MaxDB &  NaiveBayes &  0.56 &  95.37 &  -4.37 &  0.91  \\ 
 \hline 
\end{tabular}
\caption{Per label, per project, the best learner for that label. ROC value rates learner performance, compared with the ZeroR learner ( a learner which just chooses the largest category all of the time). F1 is the F-measure for that particular learner.}
\label{tab:best-learn-per-tag}
\end{table*}

@@

We applied the Mulan~\cite{mulan} library for Multi-Label learning to our data-set because intuitively, topics can have more than one label, much like how a particular source code revision can have more than one topic. Multi-label learning is more than just classifying entities with more than one label. It also includes methods for determining the performance of such techniques. The problem framed in the learners above has changed; instead of looking at the precision and recall of applying one label, we rank multiple labels at once. We must check if the full subset of labels was applied, and then how much of that subset was applied.

Another aspect of multi-label learning are micro versus macro measurements. Macro measurements are aggregated at a class or label level. Micro measurements are aggregated at a decision level. So a macro-ROC measurement is the average ROC over the ROC values for all labels, where a micro-ROC is the average ROC over all examples that were classified. Unfortunately for MaxDB, the macro-ROC values are undefined because of poor performance of one of the labels.

We have presented the results of Mulan's multi-label learners in Table \ref{tab:mulan}.  Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multi-label classifiERs (HOMER), performed the best. HOMER and BR act as a hierarchy of learners: BR is flat, while HOMER tries to build a deeper hierarchy to build a more accurate learner~\cite{mulan}. These classifiers performed better than other multi-label classifiers. They have the best micro and macro ROC scores, although their results seem comparable to the naive Bayesian learners we used in Section \ref{sec:suplabelling}.

@@

Very rarely did \textsf{exp2} and \textsf{exp3} (naive word matching) ever perform as well as the machine learners. For MaxDB, reliability was slightly better detected using the static word list of \textsf{exp2}. In general, the machine learners and \textsf{exp3} did better than \textsf{exp2} for both MaxDB and MySQL. For both MySQL and MaxDB usability was better served by \textsf{exp2}. Usability was a very infrequent label, however.
